---
  title: "exSTRa"
output: html_document
---
  
  ```{r include = FALSE}
library(viridis)
a <- 1:4
```

##Vignette exSTRa - extending the search.

After running exSTRa across the standard search -for the known loci which are specified in  ["/inst/exdata"](https://github.com/PiotrPython/exSTRa_dev//inst/exdata/repeat_expansion_disorders.txt) you might want to extend the search to other loci. The standard version run the loci which are specified [repeat_expansion_disorders.txt]().  

With exSTRa this is very easy to do all that is needed is to change two files one is perl code the other R code. The general idea is the same for both the perl code and the R code, all that changes is the file [repeat_expansion_disorders.txt](). We need to change it too [repeat_expansion_disorders_bigger.txt]().

#What to change.

Snippet to change [perlcode](https://github.com/bahlolab/Bio-STR-exSTRa/tree/master/examples/run_strexpansion_score.sh) change line marked #<<<<<<<
```{r echo=True, results=FALSE, fig.cap="\\label{fig:figs} wha who"}
# Running exSTRa

### Configuration

# Set bam_glob to a glob pattern that includes all bam files you wish to analyse.
# (multiple runs may be combined in R exSTRa later)
# You may separate globs by spaces or give full paths within the quotes.
# (For more complex cases, set in the perl command directly)
bam_glob="path/to/bams/*.bam"

# Output tab delimited file path:
output=output/exSTRa_scores.txt

# As provided from the R exSTRa package (https://github.com/bahlolab/exSTRa).
# Check that the reference matches your BAM files.

repeat_database=path/to/repeat_expansion_disorders_bigger.txt # <<<< change this file

```

Snippet to change in [Rcode](https://github.com/bahlolab/exSTRa/blob/master/examples/exSTRa_score_analysis.R) change line marked #<<<<<<<
```{r echo=True, results=FALSE}
# An example of exSTRa usage, for known STR expansion disorder loci

## ---- strexpansion_prepare
# best to load data.table before exSTRa if manipulation with data.table commands is required
library(data.table)
library(exSTRa)

knitr::opts_chunk$set(fig.width=11, fig.height=11)

# Read score data and file with loci information
str_score <- read_score (
  #file = system.file("extdata", "HiSeqXTen_WGS_PCR_2.txt", package = "exSTRa"),             # <<<<< comment out the old perl output file
  file  = "path/to/new_perl_output.txt"                                                      # <<<<< comment out the old perl output file
  #database = system.file("extdata", "repeat_expansion_disorders.txt", package = "exSTRa"),  # <<<<< comment out the old database
  database  = "path/to/repeat_expansion_disorder_bigger.txt"                                 # <<<<< add this
  groups.regex = c(control = "^WGSrpt_0[24]$", case = ""), # the group is the first regular expression (regex) to match
  filter.low.counts = TRUE
)

```


Done.

# Optional/helpful script
[Additional script] is a useful script that formats output from other functions which filter down to interesting candidate loci. For example [insert file name 2] was produced by filtering down to loci [confirm with make this makes sense] that appear to have a function in human brain tissue.

Excel is really fun [false excel is stupid](https://github.com/PiotrPython/exSTRa_dev//inst/exdatarepeat_expansion_disorders.txt)






